\chapter{\label{ch:5-testing} Testing}

%\minitoc

\section{Introduction}
Testing each part of this system involves checking primarily that outputs are what they should be (or at least as expected due to the outputs being semi-random in places), as we are handling a lot of data which is scraped from the internet, using APIs and other tools for gathering data from the internet. 


\section{Markov Chain System}
\subsection{Testing}
This involved simply testing that the program executed at the correct point and could handle both of the input sources I gave it, as well as that the Markov table is built successfully from the two types of input and the actual obtaining of these inputs also works.

\begin{center}
	\begin{tabular}{||m{15em} m{10em} m{10em} m{4em}||} 
		
		\hline
		Test Case & Expected & Actual & Status \\ [0.5ex] 
		\hline\hline
		Twitter corpora obtained& Twitter API returns search data& Twitter API returns search data& Pass\\
		\hline
		Twitter corpora parsing& All non-reply data is trimmed, only tweet text remains& URLS of images are still retained& Fail\\
		\hline
		Markov Table Building - Single text source& Table builds successfully& Table builds successfully& Pass\\
		\hline
		Markov Table Building - Twitter as Text source& Table builds successfully & Table builds successfully& Pass\\
		\hline
		Text Generates from single review input& Text is output, no runtime error& output obtained& pass\\
		\hline
		Text generates from Twitter search corpora& Text is output, no runtime error& output obtained& pass\\ [1ex] 
		\hline
	\end{tabular}
\end{center}

\subsection{Summary of Changes Made}
Images and URLS are still retained when the text is parsed so I introduced a check for hyperlinks and removed those from the text as well, since the reuse of this images and urls is not something I necessarily want.

\section{Template System}
\subsection{Testing}
\begin{center}
	\begin{tabular}{||m{15em} m{10em} m{10em} m{4em}||} 
		\hline
		Test Case & Expected & Actual & Status \\ [0.5ex] 
		\hline\hline
		IMDB Corpora Scraped& n*10 reviews scraped& n pages of reviews are scraped for a particular review& pass\\
		\hline 
		IMDB Plot Summary Scraped& A plot-summary is scraped from IMdB& Plot summary scraped successfully& pass\\
		\hline
		Metadata obtained from API& Cast, Director, Crew, Genre all scraped from TMdB & The aforementioned data is all obtained& pass\\
		\hline
		Cast and Crew sentiment assignation& Cast, crew, director sent all assigned appropriately &Odd repetition and multiple of the same text to one cast member, some members not mentioned and assigned to a sentence anyway & Fail\\
		\hline
		Adverbs and adjectives searching&An adverb or adjective is obtained from a given corpora& Either adverb or adjective is returned, unless there aren't any one available& fail\\
		\hline
		Intro templates fulfil successfully&Each pre-defined introduction section is fulfilled when asked& They all were filled succesfully& Pass\\
		\hline
		Main body templates fulfil successfully&Each pre-defined introduction section is fulfilled when asked& They all were filled succesfully& Pass\\
		\hline
		Outro templates fulfil successfully&Each pre-defined introduction section is fulfilled when asked& They all were filled succesfully& Pass\\
		\hline
		Full review text&A full review text is obtained& Full review text is indeed obtained& Pass\\ [1ex] 
		\hline
	\end{tabular}
\end{center}

\subsection{Changes Made}
Cast and crew being assigned individually tagged sentences that mentioned them was broken in a number of ways. For one, it would search for instances of either  name of a cast or crew member by spitting the name obtained from the API into a list based on where spaces occur in that name or their role. This meant that people with roles such as "The man with the hat" would be overly represented in the sample due to "The" and other common words being in their name. I included a list of names that could be removed from these acceptable names in order to mitigate this.\\
As well as this, the cast and crew members were being multiplied as it was not correctly identifying when cast and crew members had already had sentences assigned to them, so kept creating instances for them in the list. Instead of a list of actor/cast names, accompanied by a nested list of sentences that mention them with their sentiment polarity, it would mention the actor and cast member every single time, creating a much larger and much less efficient list. This was fixed so the data collection worked as intended.\\
In cases where adverbs or adjectives weren't present in the corpora provided, there was no method for handling this sentiment request. This was changed so that at the very least a basic adjective or adverb would be returned in the stead of something more interesting. "Good" or "well" would be returned in these cases, which is at least going to fulfil the template.



\section{NLG System}
\subsection{Testing}
Primarily involves testing that the new data obtained works as intended, as well as each stage in the NLG process was producing a correct result that could lead to an output.
\begin{center}
	\begin{tabular}{||m{15em} m{10em} m{10em} m{4em}||} 
		\hline
		Test Case & Expected & Actual & Status \\ [0.5ex] 
		\hline\hline
		Past Work Mining&&&\\
		\hline
		Most Important Cast/Crew&&&\\ 
		\hline
		Intro Structure&&&\\
		\hline
		Body Structure&&&\\
		\hline
		Outro Structure&&&\\
		\hline
		Intro aggregation&&&\\
		\hline
		Body aggregation&&&\\
		\hline
		Outro Aggregation&&&\\
		\hline
		Intro lexchoice&&&\\
		\hline
		Body lexchoice&&&\\
		\hline
		Outro lexchoice&&&\\
		\hline
		Referring Expressions&&&\\
		\hline
		Realisation&&&\\
		\hline	
		Full text& A full text is obtained, from start to beginning& We get a full review& Pass\\ [1ex] 
		\hline
		
	\end{tabular}
\end{center}

\subsection{Changes Made}



\section{Website Testing}
\subsection{Testing of Blog Website}
This testing mainly involved testing that aspects of the system that face the users work, as the rest can be handled by the PHPMyAdmin portal for interfacing with the database.
\begin{center}
	\begin{tabular}{||m{15em} m{10em} m{10em} m{4em}||} 
		\hline
		Test Case & Expected & Actual & Status \\ [0.5ex] 
		\hline\hline
		Create Account Submit& Account submits, database updates, pwd hashes+salts& pwd hash+salt successful& pass\\
		\hline
		Login Submit (correct details)&Login is successful&Login is successful& pass\\
		\hline
		Login Submit (incorrect details)&Login is unsuccessful&Login is unsuccessful& pass\\
		\hline
		Log Out Clicked&Account is logged out&Account is logged out&pass\\
		\hline
		Review Submit&Details are submitted into the db&Review is submitted successfully& pass\\
		\hline
		Review Edit Submit&Review is updated in database&Review is updated& Pass\\
		\hline
		Main Page Loads&Paginated data loads, review loads chronologically&Reviews load& Pass\\
		\hline
		Individual Review Loads&Review loads, comments section loads& Review and comments section load& Pass\\
		\hline
		Comments Submit&Comments insert into database for correct entry&Comments insert correctly&Pass\\
		\hline
		Comments Load&Comments load for correct entry& Comments do load& Pass\\ [1ex]
		\hline
	\end{tabular}
\end{center}


\subsection{Testing of Turing-Like Test Website}
Primarily involved checking data entry worked completely.

\begin{center}
	\begin{tabular}{||m{15em} m{10em} m{10em} m{4em}||} 
		\hline
		Test Case & Expected & Actual & Status \\ [0.5ex] 
		\hline\hline
		Data Fetches& Data for each review loads& It does& Pass\\
		\hline
		Completion of First Item&SQL executes successfully, update visible on database& Update is successful& Pass\\
		\hline
		Completion of Last Item&SQL executes successfully, visible on db& Update is successful& Pass\\ [1ex] 
		\hline
	\end{tabular}
\end{center}

\section{Twitter Bot}
\subsection{Testing of Twitter Bot}
I have mostly decided to test that the Bot runs as expected, although it only has two outputs.
\begin{center}
	\begin{tabular}{||m{15em} m{10em} m{10em} m{4em}||} 
		\hline
		Test Case & Expected & Actual & Status \\ [0.5ex] 
		\hline\hline
		Generating Promotional Tweet& Posts & Post Successfully & Pass \\ 
		\hline
		Gen promo tweet (length intentionally too long) & Doesn't post, code continues to execute & As prior& Pass\\
		\hline
		Generate Markov Tweet (Acceptable Length) & Posts & Tweet outside of character limit (far too often to be inadmissable) & fail\\
		\hline
		Gen Markov tweet (length intentionally too long) & Doesn't post, code continues to execute & As prior& Pass\\ [1ex] 
		\hline
	\end{tabular}
\end{center}

\subsection{Changes Made}
First, the bot would far more often than not attempt to create tweets that were too long to be postable using the Markov model, as it would not check for a character limit to have been exceeded due to this not being needed when simply generating Markov text. I added a parameter to check that things would work. \\
Then without my noticing, the bot would post tweets that were a single word long due to a mistake checking the tweets were less than the character limit and breaking the chain. It checked that the tweet was longer than 144 characters as a conditional for continuing, which no entry was as it was a single word to begin with, and just returned that first input.\\
